A general and efficient representation of Ancestral Recombination Graphs

### 2022-10-04 paper.tex
complete fig 5 caption

\begin{figure} \begin{center}
\includegraphics[width=\textwidth]{illustrations/inference.pdf} \end{center}
\caption{\label{fig-inferred-args} ARGs inferred by
(A) \kwarg~\citep{ignatieva2021kwarg},
(B) \argweaver~\citep{rasmussen2014genome,hubisz2020inference},
(C) \tsinfer~\citep{kelleher2019inferring},
and (D) \relate~\citep{speidel2019method}
for 11 samples of a 2.7kb region of the \textit{Drosophila melanogaster} ADH
locus~\citep{kreitman1983nucleotide}. The \argweaver\ example
is a sample from the inferred posterior distribution.
Note that the position of points on the
Y axis is that chosen for graphical clarity by the graphviz \texttt{dot}
algorithm,  rather than being
a direct measure of time. Additional notes about these ARGs.
}
\end{figure}

>>>>

\begin{figure} \begin{center}
\includegraphics[width=\textwidth]{illustrations/inference.pdf} \end{center}
\caption{\label{fig-inferred-args} ARGs inferred by
(A) \kwarg~\citep{ignatieva2021kwarg},
(B) \argweaver~\citep{rasmussen2014genome,hubisz2020inference},
(C) \tsinfer~\citep{kelleher2019inferring},
and (D) \relate~\citep{speidel2019method}
for 11 samples of a 2.7kb region of the \textit{Drosophila melanogaster} ADH
locus~\citep{kreitman1983nucleotide}. The \argweaver\ example
is a sample from the inferred posterior distribution. In each ARG,
colours are assigned to edges based on the time of the edge's child node: 
lighter colours are assigned to edges with older child
nodes, darker colours are assigned to edges with younger child nodes
Note that the position of points on the
Y axis is chosen for graphical clarity by the graphviz \texttt{dot}
algorithm, rather than as a direct measure of time.
Line width corresponds to the genomic span of the edge. Node colour
refers to the number of parents of the node: red is zero, brown is one, 
green to blue are two to N parents. The brightness
of the node is determined by the genomic span over which
the node has two or more children divided by the span where it has any
children. Edges are visualised below each ARG, where each row is an edge 
and the x axis reflects genomic position. The width of edges
thus corresponds to their genomic span. Edges
are ordered by the age of their child node, from oldest to youngest
moving down the page, with colours matching the edge colours in the ARG. 
Vertical lines indicate breakpoints between marginal trees.
}
\end{figure}
